\documentclass{article}

\usepackage{float}
\restylefloat{table}

\usepackage{booktabs}

\title{Team Contributions: POC\\\progname}

\author{\authname}

\date{}

\input{../Comments}
\input{../Common}

\begin{document}

\maketitle

This document summarizes the contributions of each team member up to the POC
Demo.  The time period of interest is the time between the beginning of the term
and the POC demo.

\section{Demo Plans}

\wss{What will you be demonstrating}

\section{Team Meeting Attendance}

\wss{For each team member how many team meetings have they attended over the
time period of interest.  This number should be determined from the meeting
issues in the team's repo.  The first entry in the table should be the total
number of team meetings held by the team.}

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Meetings}\\
\midrule
Total & 8\\
Jake Read & 8\\
Sunny Yao & 8\\
Rebecca Di Filippo & 8\\
Matthew Cheung & 8\\
\bottomrule
\end{tabular}
\end{table}

\wss{If needed, an explanation for the counts can be provided here.}

\section{Supervisor/Stakeholder Meeting Attendance}

\wss{For each team member how many supervisor/stakeholder team meetings have
they attended over the time period of interest.  This number should be determined
from the supervisor meeting issues in the team's repo.  The first entry in the
table should be the total number of supervisor and team meetings held by the
team.  If there is no supervisor, there will usually be meetings with
stakeholders (potential users) that can serve a similar purpose.}

\noindent \textbf{Supervisor's Name:} Prof. Istvan David

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Meetings}\\
\midrule
Total & 4\\
Jake Read & 4\\
Sunny Yao & 4\\
Rebecca Di Filippo & 4\\
Matthew Cheung & 4\\
\bottomrule
\end{tabular}
\end{table}

\wss{If needed, an explanation for the counts can be provided here.}

\section{Lecture Attendance}

\wss{For each team member how many lectures have they attended over the time
period of interest.  This number should be determined from the lecture issues in
the team's repo. You can find the number of lectures in the time period of
interest by looking at the
\href{https://calendar.google.com/calendar/u/0/embed?src=rnboqiaki1k2la7rpu3bn0um58@group.calendar.google.com&ctz=America/Toronto}
{Google calendar} for the capstone course.}

\wss{NOTE: There will be approximately 13 lectures between the start of class
and the POC demos}

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Lectures}\\
\midrule
Total & 13\\
Jake Read & 13\\
Sunny Yao & ?\\
Rebecca Di Filippo & 8\\
Matthew Cheung & ?\\
\bottomrule
\end{tabular}
\end{table}

Rebecca - The reason for my lower attendance was because of busy weeks with midterms and project deadlines in other courses, so I just reviewed the lecture slides instead.

\wss{If needed, an explanation for the lecture attendance can be provided here.}

\section{TA Document Discussion Attendance}

\wss{For each team member how many of the informal document discussion meetings
with the TA were attended over the time period of interest.}

\noindent \textbf{TA's Name:} Tiago de Moraes Machado


\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Lectures}\\
\midrule
Total & 3\\
Jake Read & 3\\
Sunny Yao & 3\\
Rebecca Di Filippo & 3\\
Matthew Cheung & 3\\
\bottomrule
\end{tabular}
\end{table}

\wss{If needed, an explanation for the attendance can be provided here.}

\section{Commits}

\wss{For each team member how many commits to the main branch have been made
over the time period of interest.  The total is the total number of commits for
the entire team since the beginning of the term.  The percentage is the
percentage of the total commits made by each team member.}

\begin{table}[H]
\centering
\begin{tabular}{lll}
\toprule
\textbf{Student} & \textbf{Commits} & \textbf{Percent}\\
\midrule
Total & 258 & 100\% \\
Jake Read & 54 & 21\% \\
Sunny Yao & 43 & 17\% \\
Rebecca Di Filippo & 115 & 44\% \\
Matthew Cheung & 46 & 18\% \\
\bottomrule
\end{tabular}
\end{table}

\wss{If needed, an explanation for the counts can be provided here.  For
instance, if a team member has more commits to unmerged branches, these numbers
can be provided here.  If multiple people contribute to a commit, git allows for
multi-author commits.}
Some of us commit more frequently than others, but overall work has been fairly evenly
distributed.

\section{Issue Tracker}

\wss{For each team member how many issues have they authored (including open and
closed issues (O+C)) and how many have they been assigned (only counting closed
issues (C only)) over the time period of interest.}

\begin{table}[H]
\centering
\begin{tabular}{lll}
\toprule
\textbf{Student} & \textbf{Authored (O+C)} & \textbf{Assigned (C only)}\\
\midrule
Jake Read & 0 & 3\\
Sunny Yao & 0 & 0\\
Rebecca Di Filippo & 0 & 1\\
Matthew Cheung & 0 & 0\\
\bottomrule
\end{tabular}
\end{table}

\wss{If needed, an explanation for the counts can be provided here.}
We haven't added any of our own issues, but the few closed ones are for peer reviews.
Since there's only four of us, issue tracking hasn't been a priority, and for most small tasks
we've been listing them out in Discord and assigning them informally.
Moving forward we'll use the issue tracker more, since tasks will be larger and more complex once
we get deeper into development. Sorry if this makes things hard to track, but there has been a ton
to do across all our courses and we didn't get around to making a ton of tiny issues.

\section{CICD}

\wss{Say how CICD will be used in your project}

\section{Team Charter Trigger Items}

\textbf{Trigger Summary:}  
Based on our team charter, the primary triggers for intervention include:  
\begin{itemize}
\item Missing a scheduled meeting without at least 12 hours notice  
\item Repeated missed deadlines with little or no advance communication (more than 1--2 times)  
\item Consistently arriving late without notice  
\item Not contributing adequately or submitting low-quality work  
\item Disruptive behavior or conflict without an attempt to resolve collaboratively  
\end{itemize}

\textbf{Observed Trigger Events:}  
No formal trigger violations occurred during this period. A few scheduling conflicts were communicated ahead of time and aligned with acceptable reasons outlined in the charter. These included:
\begin{itemize}
\item A member completing work after returning from vacation during reading week
\item A delayed arrival to a meeting due to transportation issues, and the meeting was shifted accordingly
\item During a long (approx 12 hours) SRS polishing work session, a member needed to attend a mandatory tutorial during the meeting and another member had prior family plans in the evening and had to leave early.
\end{itemize}
All instances were communicated prior to the meeting or work session and did not impact project progress.
\medskip{}

\textbf{Plan and Reflection:}  
No corrective action was necessary, as all situations fell under acceptable charter guidelines and were handled responsibly. The team will continue to:
\begin{itemize}
\item Communicate scheduling conflicts in advance
\item Support academic and personal commitments when reasonable
\item Maintain fairness, accountability, and consistent participation
\end{itemize}
Our current triggers appear appropriate and do not require revision at this time.


\end{document}