\documentclass{article}

\usepackage{float}
\restylefloat{table}

\usepackage{booktabs}

\title{Team Contributions: Rev 0\\\progname}

\author{\authname}

\date{}

\input{../Comments}
\input{../Common}

\begin{document}

\maketitle

This document summarizes the contributions of each team member for the Rev 0
Demo.  The time period of interest is the time between the PoC demo and the Rev
0 demo; the contributions prior to the PoC are NOT included.

\section{Demo Plans}

We plan to demonstrate a better performing Catan AI agent that uses a combination of
curriculam learning and deep reinforcement learning to play the game at a higher level.
By the time of the Rev 0 demo, we expect to be able to demonstrate the playback of an agent
beating the current best benchmark bot over 50\% of the time. This will show significant progress
over the PoC demo, where we only expected to be able to demonstrate a basic functional agent
that could play the game at all.

\section{Team Meeting Attendance}

%\wss{For each team member how many team meetings have they attended over the
%time period of interest.  This number should be determined from the meeting
%issues in the team's repo.  The first entry in the table should be the total
%number of team meetings held by the team.}

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Meetings}\\
\midrule
Total & 3\\
Jake Read & 3\\
Rebecca Di Filippo & 3\\
Sunny Yao & 3\\
Matthew Cheung & 3\\
\bottomrule
\end{tabular}
\end{table}


\section{Supervisor/Stakeholder Meeting Attendance}

%\wss{For each team member how many supervisor/stakeholder team meetings have
%they attended over the time period of interest.  This number should be determined
%from the supervisor meeting issues in the team's repo.  The first entry in the
%table should be the total number of supervisor and team meetings held by the
%team.  If there is no supervisor, there will usually be meetings with
%stakeholders (potential users) that can serve a similar purpose.}

\noindent \textbf{Supervisor's Name: } Istvan David

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Meetings}\\
\midrule
Total & 1\\
Jake Read & 1\\
Rebecca Di Filippo & 1\\
Sunny Yao & 1\\
Matthew Cheung & 1\\
\bottomrule
\end{tabular}
\end{table}

\section{Lecture Attendance}

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Lectures}\\
\midrule
Total & 1\\
Jake Read & 1\\
Rebecca Di Filippo & 0\\
Sunny Yao & 0\\
Matthew Cheung & 0\\
\bottomrule
\end{tabular}
\end{table}

Jake decided to go the the 1 lecture we had and get the notes for the rest of
the team.

\section{TA Document Discussion Attendance}

\noindent \textbf{TA's Name: } Tiago de Moraes Machado

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Lectures}\\
\midrule
Total & 0\\
Jake Read & 0\\
Rebecca Di Filippo & 0\\
Sunny Yao & 0\\
Matthew Cheung & 0\\
\bottomrule
\end{tabular}
\end{table}

Our 1 TA meeting that was scheduled was cancelled due to a snow day. 

\section{Commits}


\begin{table}[H]
\centering
\begin{tabular}{lll}
\toprule
\textbf{Student} & \textbf{Commits} & \textbf{Percent}\\
\midrule
Total &  388 & 100.0\% \\
Jake Read & 103 & 26.5\% \\
Rebecca Di Filippo & 151 & 38.9\% \\
Sunny Yao & 68 & 17.5\% \\
Matthew Cheung & 66 & 17.0\% \\
\bottomrule
\end{tabular}
\end{table}
The difference in commits isnt indicative of 
productivity or contribution. Mostly just do to commit styles,
where some people choose to commit more often than others.

\section{Issue Tracker}


\begin{table}[H]
\centering
\begin{tabular}{lll}
\toprule
\textbf{Student} & \textbf{Authored (O+C)} & \textbf{Assigned (C only)}\\
\midrule
Jake Read & 9 & 10\\
Rebecca Di Filippo & 5 & 3 \\
Sunny Yao & 6 & 2\\
Matthew Cheung & 0 & 1\\
\bottomrule
\end{tabular}
\end{table}

Some issues assigned were alot more complex than others, which can
explain the difference in numbers.

\section{CICD}

We currently have CICD set up to run tests and linting on every push to the main branch.
We also have it set up to notify us in our team chat when builds run to be able 
to keep everyone informed of the current state of the main branch (passing or failing).

\section{Team Charter Trigger Items}

\textbf{Trigger Summary:}  
Based on our team charter, the primary triggers for intervention include:  
\begin{itemize}
\item Missing a scheduled meeting without at least 12 hours notice  
\item Repeated missed deadlines with little or no advance communication (more than 1--2 times)  
\item Consistently arriving late without notice  
\item Not contributing adequately or submitting low-quality work  
\item Disruptive behavior or conflict without an attempt to resolve collaboratively  
\end{itemize}

\textbf{Observed Trigger Events:}  
No formal trigger violations occurred during this period. A few scheduling conflicts were communicated ahead of time and aligned with acceptable reasons outlined in the charter. These included:
\begin{itemize}
\item A member needing to leave a meeting early due to a prior commitment
\end{itemize}
All instances were communicated prior to the meeting or work session and did not impact project progress.
\medskip{}

\textbf{Plan and Reflection:}  
No corrective action was necessary, as all situations fell under acceptable charter guidelines and were handled responsibly. The team will continue to:
\begin{itemize}
\item Communicate scheduling conflicts in advance
\item Support academic and personal commitments when reasonable
\item Maintain fairness, accountability, and consistent participation
\end{itemize}
Our current triggers appear appropriate and do not require revision at this time.

\section{Additional Productivity Metrics}

No additional metrics were tracked during this period.

\end{document}